Exception Handling Bug Hazards in Android

### 2015-10-08 SPRINGER_JOURNAL/msr_journal.tex
including more quotes re-writting text
fixing refs

%Q1Q2_new.png
\begin{figure} \centering \includegraphics[scale=0.38]{charts/expertise.png}
\caption{Developers expertise in Java and Android development.}
\label{fig:devexpertise}
\end{figure}

@@

\textit{Exploratory Survey Studies.} Exploratory surveys have been used in the software
engineering context to discover the user perspective regarding a broad range of 
topics such as: how developers define productivity [ref]; how GitHub developers use
pull-requests[ref]; how the testing culture of open-shource projects can be characterized [ref]; 
and even how developers use Twiter [ref]. This kind of study is important as a way of 
better understanding the developers behavior and hence provide recommendations and 
tools to help on specific development tasks. This was the first exploratory survey study whose
goal was to assess developers perspective regarding a set of exception handling bug hazards
as well as how developers deal with exceptions and prevent crashes while developing.

>>>>

%Q1Q2_new.png
\begin{figure} \centering \includegraphics[scale=0.38]{charts/expertise_new.png}
\caption{Developers expertise in Java and Android development.}
\label{fig:devexpertise}
\end{figure}

@@

\textit{Exploratory Survey Studies.} Exploratory surveys have been used in the software
engineering context to discover the user perspective regarding a broad range of 
topics such as: assess the developers perceptions on productivity ~\cite{meyer2014}; 
how GitHub developers use pull-requests ~\cite{gousios2015}; 
how the testing culture of open-source projects can be characterized ~\cite{pham2013}; 
and even how developers use Twiter ~\cite{singer2014}. This kind of study is important as a way of 
better understanding the developers behavior and hence provide recommendations and 
tools to help on specific development tasks. This was the first exploratory survey study whose
goal was to assess developers perspective regarding a set of exception handling bug hazards
as well as how developers deal with exceptions and prevent crashes while developing.
